### 2014-06-10 ms/ms.Rmd
variableDefinitions gains UnitsMD column, units formatted with <sup> markdown tag. Used in ms.Rmd to format units nicely.

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
x <-daply(var.def, 1, function(x)
		paste0("* ", x$Variable,
		"\n\t- Label: ", x$label,
		"\n\t- Description: ", x$Description,
		"\n\t- Type: ", x$Type,
		"\n\t- Units: ", gsub(".","/", x$Units, fixed=TRUE)
		))

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
x <-daply(var.def, 1, function(x)
		paste0("* ", x$Variable,
		"\n\t- Label: ", x$label,
		"\n\t- Description: ", x$Description,
		"\n\t- Type: ", x$Type,
		"\n\t- Units: ", gsub(".","/", x$UnitsMD, fixed=TRUE)
		))
